\textsf{Are large language models superhuman chemists?}

### 2024-03-30 src/tex/ms.tex
done (?)

\section*{Data and code availability}
The code and data for \chembench is available at \url{https://github.com/lamalab-org/chem-bench}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}. 
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{\\showyourwork} framework.\autocite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{\GitHubURL}. 
To facilitate reproduction, some intermediate analysis results are cached at \url{http://dx.doi.org/10.5072/zenodo.34706}.

>>>>

\section*{Data and code availability}
The code and data for \chembench is available at \url{https://github.com/lamalab-org/chem-bench}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}. 
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{\showyourwork} framework.\autocite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{\GitHubURL}. 
To facilitate reproduction, some intermediate analysis results are cached at \url{http://dx.doi.org/10.5072/zenodo.34706}.
